### 2021-03-13 chapters/sections/13-imp_solution_integration.tex
Anfang und ende fertig

The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection. The IMP solution described in this chapter puts the institutions in the center of the integration in order to eliminate the need for user profiles and the need for administration portals to process personal information.

@@

As part of the existing operation of the OZG system architecture, applications submitted to administration portals will eventually be transferred to responsible governmental institutions. Using IMP, relationships can be used to send applications directly to institutions without the need for an administration portal, form server or data exchange platform.

@@

\begin{itemize}
    \item Title: Apply for administrative service XYZ
    \item Attributes: Name, Surname, ... 
    \item Shared Attributes: Institution Name ...
    \item Reason: Apply for the administrative service XYZ ...
\end{itemize}

In contrast to relationship templates in the previous IMP solution, these wont have to be dynamically created but only once. The reason is that in the previous IMP solution templates had to contain personalized information like the session ID. This is not necessary in this case.

@@

Visiting the web page of the institution, the user can scan the QR code and is presented with the relationship template. The user can read through the included description of the corresponding administrative service to determine if it is the correct one. Based on the requested attributes and the information on how they are processed, the user can make an informed decision whether to apply for the administrative service.

When sending the relationship request, the institution directly receives it without an administration portal being involved. Based on the shared attributes, the institution can decide to either accept or reject the application request. It might for example verify if the home address of the user lies in the area of its responsibility.

When accepting the relationship and therefore the application request, and the user did not retract his request in the meantime, the relationship is established and the institution gets notified about a new application.

@@

However, the administration portal cannot be completely replaced. It is still required by users for directing them to the correct institution based on the selected administrative service and for example their home address. Therefore, users visit any administration portal, search for an administrative service and specify their home address. The administration portal is able to determine the responsible institution and forward the user to an URL provided by the institution.

@@

This IMP solution utilizes the same message types as the previous IMP solution, however with a different purpose.

@@

Through the IMP, client users can request attribute changes for established relationships. The purpose of these messages is to enable users to change the content of an application even after it was submitted.

@@

As no user profiles are necessary in this IMP solution, users wont have to use the IMP client for logging into a user profile. However, authentication messages can still be used as an accept / reject based communication method.

@@

As a result of mapping IMP relationships to individual business processes, the user has more granular control of sharing personal information. Compared to the previous IMP solution, the user does not give general access to personal information for the purpose of creating a user profile but for individual processes. The user can better control whether he agrees to share personal information for processing an administrative service, while in the previous IMP solution the IMP client was not involved. In case of the OZG, the user profile component did require authentication prior to sharing attributes with institutions, but this might not be the case for all service providers.

Using relationships for execution of business processes eliminates the need for service providers to operate identity management systems. It is sufficient to integrate the identity management capabilities of the IMP system according to the IMP solution. This leaves the service provider with the main task of executing the business processes.

@@

The disadvantage of this IMP solution is, the invasive integration, which does not only provide an alternative way of accessing existing systems but for the most part replaces them.

>>>>

The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection. The IMP solution described in this chapter puts the institutions in the center of the integration in order to eliminate the need for user profiles and administration portals to process personal information.

@@

As part of the existing operation of the OZG system architecture, applications submitted to administration portals will eventually be transferred to responsible governmental institutions. Using IMP relationships can be used to send applications directly to institutions without the need for an administration portal, form server or data exchange platform.

@@

\begin{figure}[H]
\begin{itemize}
    \item Title: Apply for administrative service XYZ
    \item Attributes: Name, Surname, ... 
    \item Shared Attributes: Institution Name ...
    \item Reason: Apply for the administrative service XYZ ...
\end{itemize}
\end{figure}

In contrast to relationship templates in the previous IMP solution, these will not have to be dynamically created but only once. The reason is that in the previous IMP solution templates had to contain personalized information like the session ID. This is not necessary in this case.

@@

Visiting the web page of the institution, the user can scan the QR code and the corresponding relationship template for an application is shown. The user can read through the included description of the corresponding administrative service to determine if it is the correct one. Based on the requested attributes and the information on how they are processed, the user can make an informed decision whether to apply for the administrative service.

When sending the relationship request, the institution directly receives it without an administration portal being involved. Based on the shared attributes, the institution can decide to either accept or reject the application request. It might for example verify whether the home address of the user is within the area that it is responsible for.

When accepting the application request and therefore the whole relationship, and if the user did not retract his request in the meantime, the relationship is established and the institution gets notified about a new application.

@@

However, the administration portal cannot be completely replaced. It is still required by users for directing them to the correct institution based on the selected administrative service and for example their home address. Therefore users visiting any administration portal search for an administrative service and specify their home address. The administration portal is able to determine the responsible institution and forward the user to an URL provided by the institution.

@@

This IMP solution utilizes the same message types as the previous IMP solution, however for a different purpose.

@@

Through the IMP client, users can request attribute changes for established relationships. The purpose of these messages is to enable users to change the content of an application even after it was submitted.

@@

As no user profiles are necessary in this IMP solution, users will not have to use the IMP client for logging into a user profile. However, authentication messages can still be used as an accept / reject based communication method.

@@

As a result of mapping IMP relationships to individual business processes, the user has more granular control of sharing personal information. Compared to the previous IMP solution, the user does not give general access to personal information for the purpose of creating a user profile but for individual processes. The users can better control whether they agree to share personal information for processing an administrative service, while in the previous IMP solution the IMP client was not involved. In case of the OZG, the user profile component did require authentication prior to sharing attributes with administration portals, but this might not be the case for all Service Providers.

Using relationships for execution of business processes eliminates the need for Service Providers to operate identity management systems. It is sufficient to integrate the identity management capabilities of the IMP system according to the IMP solution. This leaves the Service Provider with the main task of executing the business processes.

@@

The disadvantage of this IMP solution is the invasive integration which does not only provide an alternative way of accessing existing systems but for the most part completely replaces them.

### 2021-03-13 chapters/sections/14-technological_integration.tex
Anfang und ende fertig

Focus of the technological integration in this case is to use the same messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions. The layout of the messaging system should not change and the purpose of each module should stay the same. In order to adapt the architecture to the new system architecture and IMP solution, the modules can be configured and named differently.

@@

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/1. Integration Overview.pdf}
\end{center}

@@

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/3. Application Overview.pdf}
\end{center}

@@

\begin{center}
    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/2. Messaging Overview.pdf}
\end{center}

@@

\subsection{Application Template Module}

\begin{center}
    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/4. Application Template Module.pdf}
\end{center}

@@

\subsection{Application Request Module}

\begin{center}
    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/5. Application Request Module.pdf}
\end{center}

@@

\subsection{Application Relationship Module}

\begin{center}
    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/6. Application Relationship Module.pdf}
\end{center}

@@

\subsection{Application Attribute Change Request Module}

\begin{center}
    \includegraphics[scale=0.5]{Diagrams/Integration Architecture 2/Technological Integration/7. Application Attribute Change Request Module.pdf}
\end{center}

@@

\subsection{Application Attribute Sync Module}

@@

\subsection{Application Mail}

@@

\subsection{Application Authentication}

@@

\subsection{Evaluation}
The integration architecture enables users to directly interact with the system architecture of the service provider for submitting applications. This eliminates the need for administration portals to process personal information.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/OZG Personal Information.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/IMP Personal Information.pdf}
\end{center}

>>>>

Focus of the technological integration is to use the same messaging system as described in section 4.2 to integrate the new IMP solution into the different system architecture of institutions. The layout of the messaging system should not change and the purpose of each module should stay the same. In order to adapt the architecture to the new system architecture and IMP solution, the modules can be configured and named differently.

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/1. Integration Overview.pdf}
    \caption{Integration Overview}
    \label{integration2:integration_overview}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/3. Application Overview.pdf}
    \caption{Service Application Overview}
    \label{integration2:application_overview}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.45]{Diagrams/Integration Architecture 2/Technological Integration/2. Messaging Overview.pdf}
    \caption{Messaging Overview}
    \label{integration2:messaging_overview}
\end{figure}

@@

\subsection{Messaging Modules}

\paragraph{Application Template Module}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/4. Application Template Module.pdf}
    \caption{Application Template Module}
    \label{integration2:application_template_module}
\end{figure}

@@

\paragraph{Application Request Module}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/5. Application Request Module.pdf}
    \caption{Application Request Module}
    \label{integration2:application_request_module}
\end{figure}

@@

\paragraph{Application Relationship Module}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/6. Application Relationship Module.pdf}
    \caption{Application Relationship Module}
    \label{integration2:application_relationship_module}
\end{figure}

@@

\paragraph{Application Attribute Change Request Module}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Technological Integration/7. Application Attribute Change Request Module.pdf}
    \caption{Application Attribute Change Request Module}
    \label{integration2:application_attribute_change_request_module}
\end{figure}

@@

\paragraph{Application Attribute Sync Module}

@@

\paragraph{Application Mail Module}

@@

\paragraph{Application Authentication Module}

@@

\subsection{Evaluation}
The integration architecture enables users to directly interact with the system architecture of the Service Provider for submitting applications. This eliminates the need for administration portals to process personal information.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/OZG Personal Information.pdf}
    \caption{OZG System Architecture Personal Information}
    \label{integration2:ozg_personal_information}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/IMP Personal Information.pdf}
    \caption{IMP System Architecture Personal Information}
    \label{integration2:imp_personal_information}
\end{figure}

### 2021-03-13 chapters/sections/15-conclusion.tex
Anfang und ende fertig

\begin{itemize}
    \item Purpose of the thesis is to design integration solutions for identity management provisioning systems on the example of OZG.
    \item The integration is separated into a business scenario integration trough an IMP solution and a system integration trough a messaging system.
    \item Trough two IMP solutions, it was shown, how IMP can be utilized in different identity management scenarios
    \item In the first scenario, an IMP solution was presented which focused on enhancing usability of 
    \item The thesis introduced identity management provisioning as an identity management service capable of replacing conventional user profiles
    \item On the example of the OZG, the thesis showed 
\end{itemize}

@@

\begin{itemize}
    \item experimental evaluation
    \item 
\end{itemize}

>>>>

The thesis describes an identity management method called IMP, which provides identity management to Service Providers and users as a service. To share personal information, users and Service Providers can establish IMP relationships and exchange IMP messages to interact with each other. On the example of the system architecture for the Online Access Law, problems of user profile based identity management are described as well as possibilities of how IMP could be used to solve them.

User profile based identity management systems lack usability as they lead to a fragmentation of partial identities, accessible only through separate applications and web pages. Data protection is reduced due to the lack of oversight for the user about existing user profiles and shared personal information. Due to the distribution of personal information to various Service Providers, the risk of data being stolen increases.

Especially in case of the OZG, issues regarding data protection exist: As a result of the "one-for-all" method, access to administrative services is distributed across multiple administration portals. Users applying for services therefore have to share large quantities of personal information with administration portals of multiple federal states. As institutions and not administration portals eventually process the personal information, sharing personal information directly with institutions would be favourable in regard to data minimisation.

Using the OZG as an example, the thesis presents two solutions for IMP utilization for Service Providers with existing user profile based identity management.
The first solution utilizes IMP in addition to existing user profiles. It provides an optional way for users to create and manage OZG user profiles through an IMP client. This is done by enabling users to create new user profiles through existing IMP identities by establishing an IMP relationship. By exchanging IMP messages users are able to access and manage their user profile. The IMP solution especially improves usability as OZG user profiles can be managed along with many other user profiles of other Service Providers through the same IMP client. The solution requires integration only with the administration portal component and can operate without disrupting the existing operation of the system architecture. However, this IMP solution does not solve many of the data protection issues, as the user profile based identity management system remains in operation.

The second solution utilizes IMP to replace user profiles. Instead of persistently sharing personal information with administration portals in form of user profiles, IMP is used to temporarily share personal information with institutions, for the period of time where an application is being processed. This is done by enabling users to establish different types of IMP relationships, each corresponding to a different application type.
This IMP solution especially improves data protection, as only the institution responsible for processing the application receives personal information. In addition to that, sharing personal information only for a short period of time decreases the risk of personal information being misused or stolen.

Service Providers which want to use IMP solutions have to integrate the IMP system into their existing system architecture.
The IMP system provides an IMP connector with a REST interface for integration purposes. However, as the functionality of the connector is limited to establishing communication between user and Service Provider and exchanging messages, additional integration systems are necessary.

The thesis presents a modular messaging system, which enables the integration of IMP solutions into existing system architectures of Service Providers. Through the messaging system, the system architecture of the Service Provider can 
establish multiple types of IMP relationships and define, exchange and process different message types. The messaging system maps relationships to entities the SP systems understand. This can be for example the mapping of an IMP relationship to a user profile or to an application process. It also translates between data models of IMP and Service Provider. As a result of using messaging and messaging modules, the integration system can be configured and extended to fit requirements of different system architectures of Service Providers.

The messaging system is shown, integrating both previously descried IMP solutions into different system architectures. The first IMP solution was integrated into the administration portal component, the second IMP solution was integrated into the institution domain. This demonstrates, that the messaging system is capable of integrating different IMP solutions into different system architectures.

\section{Solution to Objectives}

@@

The bachelor thesis describes integration of IMP on a theoretical level. Developing a prototype of the messaging system as part of an experimental evaluations can give further information about its feasibility, performance and stability. The prototype can furthermore be used to test integration of the first IMP solution into the OZG system architecture of a federal state to validate the functionality of IMP solution and messaging system and find out about possible missing features. Due to the modular design of the messaging system, new messaging modules implementing missing features can be added.

The thesis presents OZG as a Service Provider relevant for integration of IMP. IMP, however, is relevant for many other Service Providers. For example, in the scope of the National Education Platform, "a digital portal is being created that in the future will support universities as well as national and international students who are seeking a stay abroad, a course of study, or a change of study location in Germany along their educational career through a digital offering that is interoperable across institutions" \cite{digitale_bildung}. In accordance to IMP solutions in the thesis, an IMP solution for this new use case can be designed and the presented messaging system can be configured and expanded to suit new requirements and be used for system integration.

### 2021-03-13 chapters/sections/2-objective.tex
Anfang und ende fertig

Purpose of the thesis is to design an integration solution for identity management provisioning and identity management provisioning systems.

In order to make the integration suitable to real life requirements, the OZG is selected as an example due to its current relevance and high requirements regarding identity management.

Two solutions for IMP integration and one message based IMPS integration architecture are presented.

The IMP solutions describe two important fundamentally different approaches of how service providers can utilize IMP for identity management. In the first solution IMP is used alongside existing user profiles, utilizing IMP as a way of improving existing user profile based identity management solutions without replacing them. This approach is especially important for service providers in the private sector which require integration with minimal risk and cost.

In the second solution, IMP is used as an alternative way for identity management without user profiles. This approach is especially important for service providers constructing new system architectures or have strong interest in data protection and data economy.

The message based IMPS integration architecture is designed to enable integration of multiple IMP solutions into different system architectures of service providers. This is demonstrated by presenting the integration of both IMP solutions contained in the thesis, each into a different system architecture.

>>>>

Identity management systems do not stand alone but have to be accessible by various other systems in a system architecture to for example access personal information and perform authentication. They also play an important role in the design of business processes. Therefore, for Service Providers to utilize IMP, integration into existing business processes and existing system architectures is necessary.

A currently relevant topic with challenging requirements regarding identity management is the German Online Access Law (Online Zugangs Gesetz - OZG). It requires all administrative services of the German federal republic, each federal state and commune to be digitally available through interoperable user profiles. The current plan is to make user profiles only available for usage in context of the OZG. From a user perspective, this is yet another partial identity and user profile to manage.

One objective of the bachelor thesis is to design IMP solutions which enable utilization of IMP on the example of - but not limited to - the OZG use case. IMP solutions describe how IMP relationships and IMP messages can be utilized by users and Service Providers to share personal information and interact in order to improve, simplify, eliminate or replace existing business process. Besides usability and system complexity concerns, IMP solutions also make design decisions in regard to data protection and security.

Using OZG as an example, another objective of the bachelor thesis is to design a technological integration architecture for integration of IMP solutions into existing system architectures of Service Providers. Its integration capabilities should, however, not be limited to one IMP solution and one system architecture. On the contrary, it should be capable of integrating various IMP solutions into different system architectures. The integration system therefore should be configurable and expandable according to requirements of new IMP solutions and system architectures. To demonstrate the capabilities of the integration architecture, IMP solutions presented as part of the thesis, should be integrated into different system architectures in context of the OZG.

### 2021-03-13 chapters/sections/3-structure_of_work.tex
Anfang und ende fertig

In the chapter "Background and Related Work" important topics, following chapters rely on are covered.
In the chapter "User profile Identity Management" disadvantages of conventional user profile based identity management are described as well ass possible solutions trough IMP.
In the chapter "Enhancing Utilization in OZG" the first IMP solution is presented as well as its integration through the IMPS integration architecture.
In the chapter "Replacing IMP Utilization" the second IMP solution is presented as well as its integration through the IMPS integration architecture.
In the chapter "Conclusion" the most important results of the thesis are summarized and possible future developments and contributions are discussed.

>>>>

In the chapter "Background and Related Work" important topics that following chapters rely on are covered.
In the chapter "User profile Identity Management" disadvantages of conventional user profile based identity management are described as well as possible solutions through IMP.
In the chapter "Enhancing Utilization in OZG" the first IMP solution is presented as well as its integration through the IMPS integration architecture.
In the chapter "Replacing IMP Utilization" the second IMP solution is presented as well as its integration through the IMPS integration architecture.
In the chapter "Conclusion" the most important results of the thesis are summarized and possible future developments and contributions are discussed.
